Bandit Multiclass Classification

### 2018-10-12 ptf_margin.tex
in the middle of rational approximation

\section{Construction of polynomials}
Our $\phi$'s in considerations are as follows: TODO: fix the constant in phi so that it has norm at most 1.
\begin{enumerate}
\item $\phi(x) = (x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq \deg}$. This corresponds to the complete symmetric kernel $K_{\deg}$.
\item $\phi(x) = ( \sqrt{ {\deg \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$. This corresponds to the polynomial kernel
$K_{\deg}'(x,x') = (1 + \inner{x, x'})^{\deg}$.
\item $\phi(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$. This coresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
\end{enumerate}

@@

\subsection{Construction using rational functions}
\paragraph{The construction.} Define
\[
  Q(x) = \sum_{i=1}^t S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t - \frac 1 2).
\]
where function
\[
S_n^k(x) = \frac{P_n(-x)^{h(k)} - P_n(x)^{h(k)}}{P_n(-x)^{h(k)} + P_n(x)^{h(k)}} = \frac{A_n^k(x)}{B_n^k(x)},
\]
$h(k)$ is the smallest odd integer greater than $\log(2k+1)$, and $P_n(x) = (x - 1) \cdot \prod_{i=1}^n (x - 2^i)^2$.

\begin{lemma}[~\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
\end{lemma}
\begin{proof}
We consider two cases regarding the label of the example.
\end{proof}

\begin{fact}
$S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n(x)$ is in $[1, 1 + \frac 1 k]$.
\item If $x$ is in $[2^{-n}, -1]$, then $S_n(x)$ is in $[-1 - \frac 1 k, -1]$.
\item If $x$ is in $[-1, 1]$, then $|S_n(x)|$ is in $[-1, 1]$.
\item For all $x$ in $\fR$, $|B_n^k(x)| \geq \frac{2k}{2k+1} 2^{\frac{n(n-1)h(k)}2}$.
\end{enumerate}
\end{fact}

>>>>

\section{Construction of polynomials}
Our $\phi$'s in considerations are as follows: TODO: fix the constant in phi so that it has norm at most 1.
\begin{enumerate}
\item $\phi(x) = (x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq \deg}$. This corresponds to the complete symmetric kernel $K_{\deg}$.
\item $\phi(x) = ( \sqrt{ {\deg \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$. This corresponds to the polynomial kernel
$K_{\deg}'(x,x') = (1 + \inner{x, x'})^{\deg}$.
\item $\phi(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$. This corresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
\end{enumerate}

@@

\subsection{Construction using rational functions}
\paragraph{The construction.} Define
\[
  Q(x) = \sum_{i=1}^t S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t - \frac 1 2).
\]
where function
\[
S_n^k(x) = \frac{P_n(-x)^{h(k)} - P_n(x)^{h(k)}}{P_n(-x)^{h(k)} + P_n(x)^{h(k)}} = \frac{A_n^k(x)}{B_n^k(x)},
\]
$h(k)$ is the smallest odd integer greater than $\log(2k+1)$, and $P_n(x) = (x - 1) \cdot \prod_{i=1}^n (x - 2^i)^2$.
Denote by $D_i(x) = S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})$. $Q$ can therefore be simplified to 
\[ Q(x) = \sum_{i=1}^t D_i(x) - (t - \frac 1 2). \]

\begin{lemma}[~\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
\end{lemma}
\begin{proof}
We consider two cases regarding the label of the example.
\begin{enumerate}
\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \in [\gamma, 1]$. This implies that $\frac{v_i \cdot x}{\gamma} \in [1, \frac 1 \gamma]$. 
By item~\ref{item:sign-rt} of Fact~\ref{fact:newman}, we have that $D_i(x) \in [1, 1+ \frac 1 {2t}]$. 
Hence, $Q(x) \geq t - (t - \frac 1 2) \geq \frac 1 2$.

\item Suppose $y = -1$. First observe that for all $i$ in $[t]$, $\frac{v_i \cdot x}{\gamma} \in [-\frac 1\gamma, \frac 1 \gamma]$. By items~\ref{item:sign-rt},
~\ref{item:sign-lt} and~\ref{item:sign-mid} of Fact~\ref{fact:newman}, we have that $S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \leq 1+ \frac 1 {2t}$.
In addition, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$. 
By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
$D_{i_0}(x) \in [-1 - \frac 1 {2t}, -1]$.
Hence, 
\[ Q(x) = D_{i_0}(x) + \sum_{i \neq i_0} D_i(x) - (t - \frac 1 2)
\leq -1 + (t-1)(1 + \frac 1 {2t}) - (t - \frac 1 2) \leq - \frac 1 2. \]
%\leq -1 + t-1 + \frac{t-1}{2t} - (t - \frac 1 2)

\end{enumerate}
\end{proof}

\begin{fact}
$S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n^k(x)$ is in $[1, 1 + \frac 1 k]$. \label{item:sign-rt}
\item If $x$ is in $[-2^{-n}, -1]$, then $S_n^k(x)$ is in $[-1 - \frac 1 k, -1]$. \label{item:sign-lt}
\item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $\abs{B_n^k(x)} \geq 2^{\frac{n(n-1)h(k)}2 - 1}$. \label{item:sign-denom}
\end{enumerate}
\label{fact:newman}
\end{fact}
\begin{proof}
We prove all the items accordingly.
\begin{enumerate}
\item Observe that $S_n^k(x)$ can be written as:
\[ S_n^k(x) = \frac{1 + (-\frac{P_n(x)}{P_n(-x)})^{h(k)}}{ 1 - (-\frac{P_n(x)}{P_n(-x)})^{h(k)} }.  \]
Denote by $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)}$. By item~\ref{item:x-large} of Fact~\ref{fact:pn}, $r \in [0, \frac{1}{2k+1}]$. This implies that 
$S_n^k(x) = \frac{1+r}{1-r} \in [1, 1 + \frac 1 k]$.

\item The item follows from item~\ref{item:sign-rt} and the fact that $S_n^k(\cdot)$ is an odd function.

\item Note that if $x$ is in $[0, 1]$, then by item~\ref{item:x-small} of Fact~\ref{fact:pn}, $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)} \in [-1, 0]$. This implies that $S_n^k(x) = \frac{1+r}{1-r} \in [0,1]$. As $S_n^k$ is an odd function, we also have that $S_n^k(x) \in [-1, 0]$ for all $x$ in $[-1, 0]$. This proves the item.

\item If $x$ is in $[1,2^n]$, then $\abs{B_n^k(x)} = \abs{P_n(-x)^{h(k)}} (1 - r) \geq \abs{P_n(-x)^{h(k)}} \cdot \frac{2k}{2k+1} \geq 2^{\frac{n(n-1)h(k)}{2}} \cdot \frac{2k}{2k+1}$.
If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $\abs{B_n^k(x)} \geq \abs{P_n(-x)^{h(k)}} \geq 2^{\frac{n(n-1)h(k)}{2}}$. Therefore, for all $x \in [0,2^n]$, 
$\abs{B_n^k(x)} \geq \frac 1 2 2^{\frac{n(n-1)h(k)}2}$. The item is concluded by noticing that $B_n^k(x)$ is an even function.

\end{enumerate}

\end{proof}

\begin{fact}
The following is true:
\begin{enumerate}
\item If $x \in [0,1]$, then $0 \leq -P_n(x) \leq -P_n(-x)$. \label{item:x-small}
\item If $x \in [1, 2^n]$, then $0 \leq 4P_n(x) \leq -P_n(-x)$. \label{item:x-large}
\end{enumerate}
\label{fact:pn}
\end{fact}
\begin{proof}
First, observe that for any $x \geq 0$, for all $i$, $(x+2^i)^2 \geq (x - 2^i)^2$ holds.

For the first item, given that $x \in [0,1]$, $-(-x-1) \geq 1-x \geq 0$. Therefore,
\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{-(-x-1)}{1-x} \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]

For the second item, given that $x \geq 1$, $-(-x-1) \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore, 
$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
\[ \frac{-P_n(-x)}{P_n(x)} = \frac{-(-x-1)}{ x-1} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \geq 4. \]

\end{proof}
